Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-14 tex/VHzQ.tex
Minor change to filters listed in abstract

\maketitle
\begin{abstract}
We assemble a catalogue of 463 spectroscopically confirmed very high ($z\geq5.00$) redshift quasars and report their near ($zZyYJHK_{s}$ and $K$) infrared and mid-infrared (WISE) properties. We find that SDSS and Pan-STARRS1 together identified over half of the VH$z$Q sample and that 97.0\% of the VH$z$Q sample is detected in one or more NIR ($ZYJHK/K_{s}$) band, with lack of coverage rather than lack of depth for the objects that are not detected in the NIR. 362 (78.2\%) VH$z$Qs are detected at 3.4$\mu$m in the W1 band from the unWISE catalog and all of the $z\geq7$ quasars are detected in both unWISE W1 and W2. Using archival WFCAM/UKIRT and VIRCAM/VISTA data we check for photometric variability in the near-infrared that might be expected from super-Eddington accretion. We find 32 of the quasars have sufficient NIR measurements and signal-to-noise to look for variability. Weak variability was detected in multiple bands of SDSS J0959+0227, and very marginally in the $Y$-band of MMT J0215-0529. Two other quasars, SDSS J0349+0034 and SDSS J2220-0101 had significant differences between their WFCAM and VISTA magnitudes in one band. 
%% 
%% Extrapolating the known quasar luminosity function we suggest that
%% $x$\% of the possibly detected $z\geq5$ quasars in the current
%% datasets have been discovered.
All the data, analysis codes and plots used and generated here can be
found at: \href{https://github.com/d80b2t/VHzQ}{\tt
github.com/d80b2t/VHzQ}.
\end{abstract}

>>>>

\maketitle
\begin{abstract}
We assemble a catalogue of 463 spectroscopically confirmed very high ($z\geq5.00$) redshift quasars and report their near ($ZYJHK_{s}$ and $K$) infrared and mid-infrared (WISE) properties. We find that SDSS and Pan-STARRS1 together identified over half of the VH$z$Q sample and that 97.0\% of the VH$z$Q sample is detected in one or more NIR ($ZYJHK/K_{s}$) band, with lack of coverage rather than lack of depth for the objects that are not detected in the NIR. 362 (78.2\%) VH$z$Qs are detected at 3.4$\mu$m in the W1 band from the unWISE catalog and all of the $z\geq7$ quasars are detected in both unWISE W1 and W2. Using archival WFCAM/UKIRT and VIRCAM/VISTA data we check for photometric variability in the near-infrared that might be expected from super-Eddington accretion. We find 32 of the quasars have sufficient NIR measurements and signal-to-noise to look for variability. Weak variability was detected in multiple bands of SDSS J0959+0227, and very marginally in the $Y$-band of MMT J0215-0529. Two other quasars, SDSS J0349+0034 and SDSS J2220-0101 had significant differences between their WFCAM and VISTA magnitudes in one band. 
%% 
%% Extrapolating the known quasar luminosity function we suggest that
%% $x$\% of the possibly detected $z\geq5$ quasars in the current
%% datasets have been discovered.
All the data, analysis codes and plots used and generated here can be
found at: \href{https://github.com/d80b2t/VHzQ}{\tt
github.com/d80b2t/VHzQ}.
\end{abstract}
